---
title: "Challenge-5"
author: "Marzuki Nooranas"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x <- 5 

shadowing <- function() {
  x <- 10
  print(paste("Inside the function, x is:", x))
}
shadowing()

print(paste("Outside the function, x is:", x))

```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here

#this is to initiate the variable 
total <- 0

add_total <- function(number) {
  total <<- total + number
  print(paste("total is now ", total))
}

add_total(5)
add_total(5)
add_total(5)

```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here


total <- 100

add_total <- function(number) {
  total <<- total + number
  return(total)
}

new_total <- add_total(10)
sprintf ("The new total is %d", new_total)

new_total <- add_total(20)
sprintf ("The new total is %d", new_total)

new_total <- add_total(30)
sprintf ("The new total is %d", new_total)


```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here

outer_function <- function(){
  x <- 5
  inner_function <- function() {
    sprintf ("The value of x is %d", x)
  }
  inner_function()
}
outer_function()


```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(magick)
create_meme <- function(image_path, meme_text) {
  img <- image_read(image_path)
  
  # add text
  meme <- img %>%
    image_annotate(text = meme_text, 
                   gravity = 'south', 
                   location = "+0+100", 
                   size = 200, 
                   font = "Impact", 
                   strokecolor = "black", 
                   color = "white")

  
  return(meme)
}

create_meme("/Users/marzuki/Desktop/NM2207/NM2207/Week-5/meme.png", "Me after NM2207")



```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here

text_analysis_game <- function(sentence) {

  cat("Hello everyone, time for the Text Analysis Game!\n")
  cat("Analyzing the sentence:\n")
  
  # number of words
  word_count <- strsplit(sentence, " ")[[1]]
  n_words <- length(word_count)
  
  # number of char
  n_chars <- nchar(sentence)
  
  # average word length
  word_lengths <- sapply(word_count, nchar)
  avg_length <- mean(word_lengths)
  
  # statistics
  cat("\nHere are the results:\n")
  cat("Number of words:", n_words, "\n")
  cat("Number of characters:", n_chars, "\n")
  cat("Average word length:", avg_length, "\n")
  
  # Calculate a score 
  score <- (n_words * 2) + (n_chars / 10) - (avg_length * 3)
  
  # calculate score i think
  if (score < 20) {
    skill_level <- "Room for improvement. Keep practicing!"
  } else if (score >= 20 & score <= 50) {
    skill_level <- "Not bad at all! You're doing great."
  } else {
    skill_level <- "Excellent! Your communication skills are top-notch."
  }
  
  # print
  cat("Your score is:", score, "\n")
  cat("Your communication skill level is:", skill_level, "\n")
}


text_analysis_game("This is an example of the sentence maybe I could try to calculate the score")

```


<br>