---
title: "Week-5: Code-along"
author: "Marzuki Nooranas"
date: "`r Sys.Date()`"
output:
  word_document: default
  df_print: paged
  pdf_document: default
  html_document: null
pdf_document: default
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Writing a function
<br>

### 1. Write a function to print a "Hello" message (Slide #14)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
say_hello_to <- function(name) {
  print(paste0 ("Hello ", name, "!"))
}
```
<br>

### 2. Function call with different input names (Slide #15)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
myname <- "Marzuki"
say_hello_to('Kashif')
say_hello_to('Zach')
say_hello_to('Denis')
say_hello_to(myname)

```
<br>

### 3. typeof primitive functions (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
typeof(`+`)
typeof(sum)
```
<br>

### 4. typeof user-defined functions (Slide #17)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
typeof(say_hello_to)
typeof(mean)
```
<br>

### 5. Function to calculate mean of a sample (Slide #19)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
calc_sample_mean <- function(sample_size) 
  { mean(rnorm(sample_size))
}
```
<br>

### 6. Test your function (Slide #22)

```{r, eval=TRUE,echo=TRUE}
# With one input
calc_sample_mean(1000)
```
<br>
```{r, eval=TRUE,echo=TRUE}
# With vector input
calc_sample_mean(c(100, 300, 3000))
```
<br>

### 7. Customizing the function to suit input (Slide #23)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse)

sample_tibble <- tibble(sample_sizes =
                        c(100, 300, 3000))

sample_tibble %>% 
  group_by(sample_sizes) %>% 
  mutate(sample_means =
      calc_sample_mean(sample_sizes))
```
<br>

### 8. Setting defaults (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# First define the function
calc_sample_mean <- function(sample_size, 
                             our_mean=0, 
                             our_sd=1) {
  sample <- rnorm(sample_size,
                  mean = our_mean,
                  sd = our_sd)
  mean(sample)
}

# Call the function 
calc_sample_mean(sample_size = 10)
```
<br>

### 9. Different input combinations (Slide #26)

```{r, eval=TRUE,echo=TRUE}
# Enter code here 
calc_sample_mean(10, our_sd = 2)
calc_sample_mean(10, our_mean = 6)
calc_sample_mean(10, 6, 2)
```
<br>

### 10. Different input combinations (Slide #27)

```{r, eval=TRUE,echo=TRUE,error=TRUE} 
# set error=TRUE to see the error message in the output
# Enter code here 
calc_sample_mean(our_mean = 5)
```
<br>

### 11. Some more examples (Slide #28)

```{r, eval=TRUE,echo=TRUE,error=TRUE} 
# Enter code here 
add_two <- function(x) { x+2
}
add_two(4)
add_two(-34)
add_two(5.784)
```
<br>

## B. Scoping
<br>

### 12. Multiple assignment of z (Slide #36)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
z <- 1
sprintf ("The value assigned to z outside the function is %d",z)

foo <- function(z = 2) { 
z <- 3
return(z+3)
} 
foo()
```
<br>

### 13. Multiple assignment of z (Slide #37)

```{r, eval=TRUE,echo=TRUE}

z <- 1
foo <- function(z = 2) {
  z <- 3
  return(z+3) 
  }

foo(z = 4)

sprintf ("The final value of z after reassigning it to a different value inside the function is %d",z)
```
<br>