---
title: "Challenge-7"
author: "Marzuki Nooranas"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Practice:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

**Plot recreation:**

```{r, eval=TRUE,echo=TRUE}
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species)) + 
  geom_point() +
  labs(title = "Bill depth and length",
       subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
       x = "Bill depth (mm)",
       y = "Bill length (mm)",
  colour = "Species",
  caption = "Source: Palmer Station LTER / palmerpenguin package") +
scale_colour_viridis_d()
```

**Palmer Penguins: Argument names:**

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins,
    aes(x = bill_depth_mm,
        y = bill_length_mm,
        colour= species)) + 
  geom_point() +
  labs(title = "Bill depth and length",
       subtitle = "Dimensions for Adelie,
       Chinstrap, and Gentoo Penguins",
       x = "Bill depth (mm)",
       y = "Bill length (mm)",
  colour = "Species",
  caption = "Source: Palmer Station LTER / palmerpenguin package") +
scale_colour_viridis_d()
```

**Palmer Penguins:Aesthetics Options:**

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
shape = species, size = body_mass_g, alpha = flipper_length_mm)) +
geom_point() + scale_colour_viridis_d()
```

**Mapping:**

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      y = bill_length_mm,
      size = body_mass_g,
      alpha = flipper_length_mm) +
geom_point()
```

**Setting:**

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      y = bill_length_mm) +
  geom_point(size = 2, alpha = 0.5)
```

**Faceting:**

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      y = bill_length_mm) +
  geom_point() +
  facet_grid(species ~ island)
```


**Facet 2:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm)) + 
  geom_point() +
facet_grid(species ~ sex)
```


**Facet 3:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm)) + 
  geom_point() +
facet_grid(sex ~ species)

```


**Facet 4:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm)) + 
  geom_point() +
facet_wrap(~ species)

```


**Facet 5:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm)) + 
  geom_point() +
facet_wrap(~ species, ncol = 2)

```


**Facet 6:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm)) + 
  geom_point() +
facet_grid(. ~ species)

```


**Facet and Colour:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm, 
           color = species)) +
geom_point() + 
  facet_grid(species ~ sex) + 
  scale_color_viridis_d()
```


**Face and color, no legend:**
```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, 
       aes(x = bill_depth_mm, 
           y = bill_length_mm, 
           color = species)) +
geom_point() + 
  facet_grid(species ~ sex) + 
  scale_color_viridis_d() +
guides(color = "none")
```

**Dataset 2: Lending Club**

```{r, eval=TRUE,echo=TRUE}
library(openintro)
glimpse(loans_full_schema)
```


**Selected Variable:**
```{r, eval=TRUE,echo=TRUE}
loans <- loans_full_schema %>%
  select(loan_amount, interest_rate, term, grade,
         state, annual_income, homeownership, debt_to_income)
glimpse(loans)

```


**Histogram**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans) + 
  aes(x = loan_amount) +
geom_histogram()

```

**Histograms and binwidth=1000:**

```{r, eval=TRUE,echo=TRUE}

# binwidth = 1000
ggplot(loans, 
       aes(x = loan_amount)) +
geom_histogram(binwidth = 1000)
```

**Customising Histogram**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, 
       aes(x = loan_amount, 
           fill = homeownership)) +
geom_histogram(binwidth = 5000, alpha = 0.5) +
labs(x = "Loan amount ($)",
     y = "Frequency",
     title = "Amounts of Lending Club loans")
```


**Facet with a categorical Variable:
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, 
       aes(x = loan_amount, fill = homeownership)) + 
  geom_histogram(binwidth = 5000) +
labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
facet_wrap(~ homeownership, nrow = 3)
```

**Density Plot:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density()
```

**Density Plot and adjusting bandwidth:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 0.5)
```

**Customising density plots:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
geom_density(adjust = 2) +
labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
geom_density(adjust = 2, alpha = 0.5) +
labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```

**Box plots:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +
geom_boxplot()
```

**Box plots and outliers:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = annual_income)) +
geom_boxplot()
```

**Customising Box Plots:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, 
       aes(x = interest_rate)) +
  geom_boxplot() +labs(x = "Interest rate (%)",
                       y = NULL,
title = "Interest rates of Lending Club loans") +
theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```

**Scatterplot:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, 
       aes(x = debt_to_income, y = interest_rate)) +
geom_point()
```

**Hex plot:**
```{r, eval=TRUE,echo=TRUE}
library(hexbin)
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
geom_hex()
```

**Hex plot 2:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans %>% 
         filter(debt_to_income < 100),
aes(x = debt_to_income, 
    y = interest_rate)) +
geom_hex()
```

**Bar plot**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership)) +
geom_bar()
```

**Segmented bar plot:**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, 
       aes(x = homeownership,
           fill = grade)) +
geom_bar()

ggplot(loans, aes(x = homeownership, 
                  fill = grade)) +
geom_bar(position = "fill")
```

**Customising Bar plots**

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", 
      y = "Homeownership", fill = "Grade", 
      title = "Grades of Lending Club loans")
```

**Violin plots**
```{r, eval=TRUE,echo=TRUE}
ggplot(loans, 
       aes(x = homeownership, y = loan_amount)) +
geom_violin()
```


**Ridge plots:**
```{r, eval=TRUE,echo=TRUE}
library(ggridges)
ggplot(loans, aes(x = loan_amount, 
                  y = grade, 
                  fill = grade, 
                  color = grade)) +
geom_density_ridges(alpha = 0.5)
```

