---
title: "Week-4: Code-along"
author: "Marzuki Nooranas"
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
pdf_document: default
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Data Wrangling
<br>

### 1. Loading packages (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Load package tidyverse
library(tidyverse)
```

### 2. Loading data-set (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Read data from the hotels.csv file and assign it to a variable named, "hotels"
hotels <- read_csv("hotels.csv")
```

### 3. List names of the variables in the data-set (Slide #19)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
names(hotels)
```


### 4. Glimpse of contents of the data-set (Slide #20)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
glimpse(hotels)
```
<br>

## B. Choosing rows or columns
<br>

### 5. Select a single column (Slide #24)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels, lead_time)
```

### 6. Select multiple columns (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels, lead_time,agent,market_segment)
```

### 7. Arrange entries of a column (Slide #28)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels, lead_time)
```

### 8. Arrange entries of a column in the descending order (Slide #30)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels, desc(lead_time))
```

### 9. Select columns and arrange the entries of a column (Slide #31)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(select(hotels, lead_time),desc(lead_time))
```

### 10. Select columns and arrange the entries of a column using the pipe operator (Slide #37)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% select(lead_time) %>% arrange(desc(lead_time))
```

### 11. Pick rows matching a condition (Slide #44)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% filter(children >= 1) %>% select(hotel, children)
```

### 12. Pick rows matching multiple conditions (Slide #46)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% 
  filter(children >= 1,hotel == "City Hotel") %>% 
  select(hotel, children)
```

### 13. Non-conditional selection of rows: sequence of indices (Slide #49)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% slice(1:5)
```

### 14. Non-conditional selection of rows: non-consecutive/specific indices (Slide #50)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  slice(1,3,5)
```

### 15. Pick unique rows using distinct() (Slide #52)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% distinct(hotel)
```
<br>

## C. Creating new columns
<br>

### 16. Creating a single column with mutate() (Slide #56)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  mutate(little_ones = children + babies) %>%
    select(hotel, little_ones,children,babies)
```

### 17. Creating multiple columns with mutate() (Slide #58)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  mutate(little_ones = children + babies,
          average_little_ones = mean(little_ones)) %>%
    select(hotel, little_ones,children,babies, average_little_ones)
```
<br>

## D. More operations with examples
<br>

### 18. count() to get frequencies (Slide #60)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  count(market_segment)
```

### 19. count() to get frequencies with sorting of count (Slide #61)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% count(market_segment, sort = TRUE)
```

### 20. count() multiple variables (Slide #62)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  count(hotel, market_segment)
```

### 21. summarise() for summary statistics (Slide #63)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  summarise(mean_adr = mean(adr))
```

### 22. summarise() by using group_by to find mean (Slide #64)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  group_by(hotel) %>%
  summarise(mean_adr = mean(adr))
```

### 23. summarise() by using group_by to get count (Slide #65)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  group_by(hotel) %>%
  summarise(count = n())
```

### 24. summarise() for multiple summary statistics (Slide #67)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  summarise(
    min_adr = min(adr),
    mean_adr = mean(adr),
    median_adr = median(adr),
    max_adr = max(adr)
)
```

### 25. select(), slice() and arrange() (Slide #68)

```{r, eval=TRUE,echo=TRUE}
hotels %>%
  select(hotel, lead_time) %>%
  slice(1:5) %>%
  arrange(lead_time)

```

### 26. select(), arrange() and slice() (Slide #69)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  select(hotel, lead_time) %>%
  arrange(lead_time) %>%
  slice(1:5)
```

### 27. filter() to select rows based on conditions (Slide #73)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  filter(adults == 0,
         children >= 1
    ) %>%
  select(adults, babies, children)
```

### 28. filter() to select rows based on complicated conditions (Slide #74)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  filter( adults == 1,
    children >= 1 | babies >=1) %>% # | means OR select(adults, babies, children)
  select(adults, babies, children)
```

### 29. count() and arrange() (Slide #76)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% count(market_segment) %>% arrange(desc(n)) # <-- decreasing order of counts
```

### 30. mutate(), select() and arrange() (Slide #77)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
mutate(little_ones = children + babies) %>% # <--- 
  select(children, babies, little_ones) %>%
  arrange(desc(little_ones))
```


### 31. mutate(), filter() and select() (Slide #78)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>%
  mutate(little_ones = children + babies) %>%
  filter(
    little_ones >= 1,
    hotel == "Resort Hotel"
    ) %>%
  select(hotel, little_ones)


hotels %>%
  mutate(little_ones = children + babies) %>%
  filter(
    little_ones >= 1,
    hotel == "City Hotel"
    )  %>%
  select(hotel, little_ones)
```